---
title: "Study 2"
subtitle: "Assumptions tests"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    toc: yes
    toc_float: yes
---

```{r include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Dependencies 

```{r}

# dependencies
library(tidyverse)
library(strengejacke)  # library(devtools); install_github("strengejacke/strengejacke")
library(knitr)
library(kableExtra)
library(psych)
library(janitor)

# make directory
dir.create("plots")

```

# Get data

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv") %>%
  mutate(condition = fct_relevel(condition, "Negative", "Neutral", "Positive"))

data_processed_after_exclusions <- data_processed %>%
  filter(exclude == FALSE) %>%
  mutate(id = as.factor(id))

```

# Sample

## Sample sizes

### Exclusions

Greater than 10% missing data on the baseline MASS scales or failed attention checks

```{r}

data_processed %>%
  count(exclude, missing = exclude_participant_based_on_missingness, 
        sexuality = exclude_participant_non_heterosexual)

data_processed %>%
  count(exclude) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Pre-post after exclusions

```{r}

data_processed_after_exclusions %>%
  count() %>%
  arrange() %>%
  kable()  %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## Demographics

After exclusions.

Sexuality not reported as non-heterosexuality was an exclusion criterion.

```{r}

data_processed_after_exclusions %>%
  summarize(mean_age = mean(age, na.rm = TRUE),
            sd_age = sd(age, na.rm = TRUE)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable()  %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_processed_after_exclusions %>%
  count(gender) %>%
  kable()  %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

data_processed_after_exclusions %>%
  count(ethnicity) %>%
  arrange(desc(n)) %>%
  kable()  %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Internal consistency

of MASS

## MASS

### Version A

```{r}

results_alpha_mass_a <- data_processed_after_exclusions %>%
  filter(task_order == "MASS & SD form A first") %>%
  select(starts_with("mass_pre_"), -mass_pre_sum_score) %>%
  alpha(., check.keys = FALSE)

results_alpha_mass_a$total["raw_alpha"] %>%
  mutate_all(round, digits = 2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Version B

```{r}

results_alpha_mass_b <- data_processed_after_exclusions %>%
  filter(task_order == "MASS & SD form B first") %>%
  select(starts_with("mass_pre_"), -mass_pre_sum_score) %>%
  alpha(., check.keys = FALSE)

results_alpha_mass_b$total["raw_alpha"] %>%
  mutate_all(round, digits = 2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## SD

### Version A

```{r}

results_alpha_sd_a <- data_processed_after_exclusions %>%
  filter(task_order == "MASS & SD form A first") %>%
  select(starts_with("sd_pre_"), -sd_pre_sum_score) %>%
  alpha(., check.keys = FALSE)

results_alpha_sd_a$total["raw_alpha"] %>%
  mutate_all(round, digits = 2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

### Version B

```{r}

results_alpha_sd_b <- data_processed_after_exclusions %>%
  filter(task_order == "MASS & SD form B first") %>%
  select(starts_with("sd_pre_"), -sd_pre_sum_score) %>%
  alpha(., check.keys = FALSE)

results_alpha_sd_b$total["raw_alpha"] %>%
  mutate_all(round, digits = 2) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Test moderation

## All participants

### Fit model

```{r}

fit_all <- lm(mass_post_sum_score ~ mass_pre_sum_score * condition,
              data = data_processed)

tab_model(fit_all, 
          show.std = TRUE,
          emph.p = FALSE,
          col.order = c("est", "se", "ci", "std.est", "std.ci", "p"))

plot_model(fit_all, type = "int")

```

### Assumption tests

```{r}

assumptions_plots_all <- plot_model(fit_all, type = "diag") 

```

#### Normality of residuals

```{r}

plot_QQ_all <- assumptions_plots_all[[2]] +
  theme_classic() + 
  labs(title = NULL,
       subtitle = NULL) +
  ylab("Sample") +
  xlab("Theoretical")

plot_QQ_all

ggsave(plot     = plot_QQ_all,
       device   = "pdf",
       filename = "plot_QQ_all.pdf",
       path     = "plots/",
       units    = "in",
       width    = 6,
       height   = 6)

```

#### Homoscedasticity

```{r}

plot_homoscedasticity_all <- assumptions_plots_all[[4]] +
  theme_classic() + 
  labs(title = NULL,
       subtitle = NULL)

plot_homoscedasticity_all

ggsave(plot     = plot_homoscedasticity_all,
       device   = "pdf",
       filename = "plot_homoscedasticity_all.pdf",
       path     = "plots/",
       units    = "in",
       width    = 6,
       height   = 6)

```


## After exclusions

### Fit model

```{r}

fit_after_exclusions <- lm(mass_post_sum_score ~ mass_pre_sum_score * condition,
              data = data_processed_after_exclusions)

tab_model(fit_after_exclusions, 
          show.std = TRUE,
          emph.p = FALSE,
          col.order = c("est", "se", "ci", "std.est", "std.ci", "p"))

plot_model(fit_after_exclusions, type = "int")

```

### Assumption tests

```{r}

assumptions_plots_after_exclusions <- plot_model(fit_after_exclusions, type = "diag") 

```

#### Normality of residuals

```{r}

plot_QQ_after_exclusions <- assumptions_plots_after_exclusions[[2]] +
  theme_classic() + 
  labs(title = NULL,
       subtitle = NULL) +
  ylab("Sample") +
  xlab("Theoretical")

plot_QQ_after_exclusions

# ggsave(plot     = plot_QQ_after_exclusions,
#        device   = "pdf",
#        filename = "plot_QQ_after_exclusions.pdf",
#        path     = "plots/",
#        units    = "in",
#        width    = 6,
#        height   = 6)

```

#### Homoscedasticity

```{r}

plot_homoscedasticity_after_exclusions <- assumptions_plots_after_exclusions[[4]] +
  theme_classic() + 
  labs(title = NULL,
       subtitle = NULL)

plot_homoscedasticity_after_exclusions

# ggsave(plot     = plot_homoscedasticity_after_exclusions,
#        device   = "pdf",
#        filename = "plot_homoscedasticity_after_exclusions.pdf",
#        path     = "plots/",
#        units    = "in",
#        width    = 6,
#        height   = 6)

```





# Robustness test

Moderation test on ranks

## All participants

```{r}

data_subset_all <- data_processed %>%
  #filter(condition %in% c("Positive", "Negative")) %>%
  mutate(rank_mass_pre_sum_score = rank(mass_pre_sum_score),
         rank_mass_post_sum_score = rank(mass_post_sum_score)) 

fit_all <- 
  lm(rank_mass_post_sum_score ~ rank_mass_pre_sum_score * condition,
      data = data_subset_all)

tab_model(fit_all,
          emph.p = FALSE,
          col.order = c("est", "se", "ci", "p"))

summary(fit_all)

plot_model(fit_all, type = "int")

```

## After exclusions

```{r}

data_subset_after_exclusions <- data_processed_after_exclusions %>%
  #filter(condition %in% c("Positive", "Negative")) %>%
  mutate(rank_mass_pre_sum_score = rank(mass_pre_sum_score),
         rank_mass_post_sum_score = rank(mass_post_sum_score))

assumptions_plots_after_exclusions <- 
  lm(rank_mass_post_sum_score ~ rank_mass_pre_sum_score * condition,
      data = data_subset_after_exclusions)

tab_model(assumptions_plots_after_exclusions,
          emph.p = FALSE,
          col.order = c("est", "se", "ci", "p"))

summary(assumptions_plots_after_exclusions)

plot_model(assumptions_plots_after_exclusions, type = "int")

```



